Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-28 manuscript/manuscript.Rmd
colors, caption

```{r}
#| label: action-X
#| fig.cap: "TBD"
#| out.width: "6.5in"
opt_escapement_harvest <- function(X) case_when(
  X > best_e ~ X - best_e,
  X <= best_e ~ 0
)

py <- ppo_df |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, harvest = action*X) |>
  ggplot(aes(X, harvest, color = Y)) +
  geom_point() +
  theme(aspect.ratio = 1/1) +
  stat_function(fun = opt_escapement_harvest, col = 'red')

pz <- ppo_df |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, harvest = action*X) |>
  ggplot(aes(X, harvest, color = Z)) +
  geom_point() +
  theme(aspect.ratio = 1/1) +
  stat_function(fun = opt_escapement_harvest, col = 'red')

(py | pz) + plot_annotation(tag_levels = c('A'))
```

>>>>

```{r}
#| label: action-X
#| fig.cap: "(A-B) Harvest and escapement scatter data for the DRL policy together with the optimal constant escapement (pink) and constant mortality (green) policies for comparison. 
#| (A) includes $Y$ dependence through color, whereas (B) includes $Z$ dependence similarly.
#| (B-C) escapement (i.e. $X_t - h_t$) scatter data for the DRL policy. 
#| Optimal constant escapement policy shown in pink for comparison."
#| out.width: "6.5in"
opt_escapement_harvest <- function(X) case_when(
  X > best_e ~ X - best_e,
  X <= best_e ~ 0
)

opt_escapement_escapement <- function(X) case_when(
  X <= best_e ~ X,
  X > best_e ~ best_e
)

msy_harvest <- function(X) best_action*X
tac_harvest <- function(X) 0.8*msy_harvest(X)

py <- ppo_df |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, harvest = action*X) |>
  ggplot(aes(X, harvest, color = Y)) +
  geom_point() +
  theme(aspect.ratio = 1/1) +
  stat_function(fun = opt_escapement_harvest, col = 'deeppink', size = 0.8) + 
  stat_function(fun = msy_harvest, col = 'seagreen2', size = 0.8)

pz <- ppo_df |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, harvest = action*X) |>
  ggplot(aes(X, harvest, color = Z)) +
  geom_point() +
  theme(aspect.ratio = 1/1) +
  stat_function(fun = opt_escapement_harvest, col = 'deeppink', size = 0.8) + 
  stat_function(fun = msy_harvest, col = 'seagreen2', size = 0.8)

escxy <- ppo_df |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, escapement = (1-action)*X) |>
  ggplot(aes(X, escapement, color = Y)) +
  geom_point() +
  theme(aspect.ratio = 1/1) +
  stat_function(fun = opt_escapement_escapement, col = 'deeppink', size = 0.8)

escxz <- ppo_df |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, escapement = (1-action)*X) |>
  ggplot(aes(X, escapement, color = Z)) +
  geom_point() +
  theme(aspect.ratio = 1/1) +
  stat_function(fun = opt_escapement_escapement, col = 'deeppink', size = 0.8)

((py | pz)/ (escxy | escxz)) + plot_annotation(tag_levels = c('A'))
```
